Individual Variation in Animal Movement and Effects on Seed Dispersal Distance

### 2021-01-10 paper/paper.Rmd
comments after reading on extreme value distributions

@@

- Already fit the weibull distribution for this. I have

@@

>>>>

*Include table in the supplement with the movement rates*

@@

- Already fit the weibull distribution for this. Mention that we chose this distribution because it is commonly used in dispersal ecology due to its felixibility, how adjusting the scale parameter changes the tail of the distribution. This is both in Garcia2017 (>1 fast decaying, <1 low decay fat tail, =1 exponential decay) and Carlomorales2006 papers, but I think they present it slightly different.

- We inspected the QQ plots to check for fitting. Figuere Supplement

- They mention declustering the data, and perhaps in that case I could be using the mean_xy_dispersal.

@@

Explain what are statistics of extremes and why they can be useful here. cite the GArcia 2017 paper, the Gaines and Denny 1993, Katz 2005. Coles 2001 for the theory or base knowledge. In our case, because we are looking at these simulated seed dispersal kernels, we use a peak over threshold (POT) approach, in which we find the threshold for the data and use an extreme value distribution to fit the tail. 
Describe the math probabilty density functions and the three laws that the extreme value distribution follows. 
For POT use a generalized pareto distribution.

- Based on Diagnostic plots, we used these values as the threshold for each of the models.
